---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# discountr

<!-- badges: start -->
<!-- badges: end -->

The goal of discountr is to provide data analysis tools for discounting studies.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mncube/discountr")
```
## Example

This is a basic example which shows you how to compute the area under the empirical discounting function using the trapezoid approximation as described
in: 

Myerson, J., Green, L., & Warusawitharana, M. (2001). Area under the curve as a measure of discounting. Journal of the experimental analysis of behavior, 76 2, 235-43 .
```{r example}
library(discountr)

#Create data frame with successive delays and subjective values
df_disc <- data.frame(delay = sample(1:100, 50, replace = FALSE),
                      value = sample(1:100, 50, replace = TRUE))

#Normalize data in preparation for the auc calculation
#This will ensure that the auc is between 0 and 1
df_disc$delay <- df_disc$delay/max(df_disc$delay)
df_disc$value <- df_disc$value/max(df_disc$value)

#Calculate the area under the curve
output_disc <- trap_auc(df_disc, x = delay, y = value)

#Get the total area under the curve (i.e., sum over trapezoids)
output_disc$total

#Get the data frame containing the area under the curve for each trapezoid
output_disc$data
```

You can also convert the data frame to trapazoidal form and then explicitly provide
the x_lead and y_lead values when computing the area under the empirical discounting function: 
```{r}
#Create data frame with successive delays and subjective values
df_disc_2 <- data.frame(delay = sample(1:100, 50, replace = FALSE),
                      value = sample(1:100, 50, replace = TRUE))

#Normalize data in preparation for auc calculation
df_disc_2$delay <- df_disc_2$delay/max(df_disc_2$delay)
df_disc_2$value <- df_disc_2$value/max(df_disc_2$value)

#Reformat data in preparation to compute the trapezoidal auc
#The resulting data frame will have two new columns:
#delay_lead and value_lead
df_disc_2 <- traper(df_disc_2, x = delay, y = value, rename = TRUE)

#Calculate the area under the curve explicitly defining x_lead and y_lead
output_disc_2<- trap_auc(df_disc_2, x = delay, y = value,
                          x_lead = delay_lead, y_lead = value_lead)

#Get the total area under the curve (i.e., sum over trapezoids)
output_disc_2$total

#Get the data frame containing the area under the curve for each trapezoid
output_disc_2$data
```
